%  For credit to source, please look at the readme.txt file. 

%   We suggest to 
    %  Start all bullet item items with action verbs. You may base form or ing form or verbs where suited. See action verbs here, https://ecs.ihu.edu.gr/co/employment-cvcletter/action-verbs.html
    %  Provide the most relevant information
    %  Provide evidence for your skills.  For example, if you include MS Office and Python in your skills list, then provide bullet points detailing what YOU can do in MS Office and Python.  
    %  In each section--start entries with the most recent one
    %  Pay attention to grammar, avoid typos
    %  Avoid using abbreviations
    %  If you're applying for jobs, put your experience and skills before education
    %  Some examples of presentations are provided


\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} 
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
    a4paper,
    top=1.8cm,
    bottom=1in,
    left=2.5cm,
    right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

%== HEADER ==%
\begin{center}      
    {\fontsize{28}{28}\selectfont Larissa Silva de Souza Neitzke} \\ \bigskip

    {\color{icnclr}\faMapMarker} São Leopoldo, Brazil \quad 
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:myaname@email.com}{larissasouza.neitzke@gmail.com} \quad
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:+920000000000}{+55 51 999358135} 
    % You can also put your LinkedIn or website address
   % {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/}{linkedin.com/in/username}
\end{center}
%==============
%==============
%==============
\section{About me}
%==============
%==============
I am a programming student passionate about technology and innovation, looking for my first internship to apply my knowledge in Systems Development and contribute to creative and efficient solutions. 
%==============
%==============
\section{Education}
%==============
%==============
%==============
%==============
\subsection{Technologist in Systems Development\hfill \normalfont 2024-Current}  

\subsubsection{SENAC-RS,  São Leopoldo, Brazil}
\begin{itemize}
    \item[\checkmark] \textit{GPA}: 3.8/4.0
    \item[\checkmark] \textit{Related coursework}: Mathematical modelling and numerical analysis
    \item[\checkmark] \textit{Thesis:} Write title of your thesis
    \end{itemize}
%==============
%==============
\subsection{Graduate Course in Digital Law, Cybersecurity and AI\hfill \normalfont 2024-Current}  

\subsubsection{Fundação Escola Superior do Ministério Público - FMP,  Porto Alegre, Brazil}
\begin{itemize}
    \item[\checkmark] \textit{GPA}: 3.52/4.0
    \item[\checkmark] \textit{Related coursework}: Major in Mathematics with minor courses in Physics, Probability and Statistics
    \item[\checkmark] \textit{Thesis:} Write title of your thesis (if any)
    \end{itemize}
%==============
%==============
\subsection{Bachelor’s Degree in Law\hfill \normalfont 2013-2018}  

Universidade do Vale do Rio dos Sinos - UNISINOS,  São Leopoldo, Brazil}
\begin{itemize}
    \item[\checkmark] \textit{GPA}: 3.52/4.0
    \item[\checkmark] \textit{Related coursework}: Major in Mathematics with minor courses in Physics, Probability and Statistics
    \item[\checkmark] \textit{Thesis:} Write title of your thesis (if any)
    \end{itemize}
    
%==============
%==============
\section{Skills}
%==============
%==============
\subsection{Computational}
\begin{itemize}
    \item[\checkmark] Atlassian Jira.  
    \item[\checkmark] Atlassian Confluence. 
    \item[\checkmark] Microsoft Excel. 
    \item[\checkmark] MySQL.  
    \item[\checkmark] SQL.
\end{itemize}
\subsection{Languages}
\begin{itemize}
    \item[-] \textcolor{Sepia}{Portuguese}: Mother tongue
    \item[-] \textcolor{Sepia}{English}: Very good
    \item Spanhish: Basic
    \end{itemize}

%==============
%==============
\section{Experience}
%==============
%==============
\subsection{RS2 Software (Remotely - Malta/EU) \hfill \normalfont Feb 2020 -- Current}
\subsubsection{Mosta, Malta}
% Start all items with action verbs
\begin{itemize}
    \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
    \item[\checkmark]  Developed XYZ using ABC that led to X\% improvement 
    \item[\checkmark] Solved ABC with AAA method leading to CCC.
    \item[\checkmark]  Accomplished XYZ feature to accomplish ABC.
    \item[\checkmark]  Implemented XYZ library for ABC.
\end{itemize}

\subsection{Role Name \hfill \normalfont Jan 20XX - Feb 20XY}
\subsubsection{Company Name, City, Country}
% Start all items with action verbs
\begin{itemize}
    \item[\checkmark] Implemented XYZ method - Accomplished [X] as measured by [Y], by doing [Z] 
    \item[\checkmark]  Developed XYZ using ABC that led to X\% improvement 
    \item[\checkmark] Solved ABC with AAA method leading to CCC.
    \item[\checkmark]  Accomplished XYZ feature to accomplish ABC.
    \item[\checkmark]  Implemented XYZ library for ABC.
\end{itemize}
%==============
%==============
%==============
%==============
\section{Certifications \& Awards}
%==============
% Mentioned most important certificates where you have received some training or award or have delivered a presentation
%==============
\begin{itemize}
    \item[\checkmark] Microsoft Excel - Excel from Beginner to Advanced (Udemy, 2020)
    \item[\checkmark] English Course - B1/B2 (English Domain, 2019)
\end{itemize}
%==============
%==============
%==============
%==============
\section{References}
\textcolor{Sepia}{References available upon request.}
\end{document}
